On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
chaz

\begin{corollary}
Unsupervised neurally plausible sparse feature learning through a wiring bottleneck recovers original sensory representations and neural activities.
\end{corollary}

>>>>

\begin{corollary}
Unsupervised neurally plausible sparse feature learning through a wiring bottleneck recovers neural activities representing original sensory stimuli.
\end{corollary}
